%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{\href{https://drive.google.com/file/d/1GJMpTmXE6hE0hE4XFeh3W5B-CXobKz1r/view?usp=sharing}{Hackathons}}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {Smart India Hackathon (Hardware)} % Project Title
	{Selected for the project Anti pilferage and anti adulteration system for fuel road tankers.} % Description
	{IISC, Bangalore} % Location
	{May. 2018} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://drive.google.com/file/d/1pZPRlO3d-uHbwj0PD--kGmI6AiCMTnAV/view?usp=sharing}{Smart India Hackathon (Software)}} % Project Title
	{Selected for the project Collection of water quality data observed by private organizations.} % Description
	{BHU, Varanasi} % Location
	{Mar. 2018} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://drive.google.com/drive/folders/1aT_wiJboLKDqXjuD8641xuNuK67zotdx?usp=sharing}{Rajasthan Hackathon 3.0 (Digifest)}} % Affiliation/role
	{Leader, Selected for the hardware project Plant Monitorisation.} % Organization/group
	{Udaipur} % Location
	{Dec. 2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://drive.google.com/file/d/1m6jinRih9FB5npqilY9bRInptfyr0_eD/view?usp=sharing}{World Food India Hackathon} (MoFPI)} % Affiliation/role
	{Selected for the project Regional Culinary Mobile application. The only team selected from Rajasthan State. \href{https://blog.mygov.in/announcing-shortlisted-entries-for-world-food-india-hackathon-2017-final-round/}{mygov blog}} % Organization/group
	{New Delhi} % Location
	{Oct. 2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://drive.google.com/file/d/1awN5B-bK9bPXvUSInTCRrdPGwepkewyC/view?usp=sharing}{OpenGovData Hackathon}} % Affiliation/role
    {Selected for the project BloodBank tracker application created using government open data.} % Organization/group
    {Jaipur} % Location
    {Oct. 2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://drive.google.com/file/d/1fvv7lMfpzCRUohSPCJd6jZ30_8Or_YJQ/view?usp=sharing}{Smart India Hackathon (MoES)} } % Affiliation/role
    {Selected for the project digitalisation of Andaman \& Nicobar Islands. } % Organization/group
    {SRM, Chennai} % Location
    {\href{https://innovate.mygov.in/sih2017/}{Apr. 2017}} % Date(s)

%---------------------------------------------------------
\end{cvhonors}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{College}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
	{\href{https://www.facebook.com/citabuinfo/posts/1229195450520361}{Engineer's Day}}% Affiliation/role
	{Leader, Winner of the Engineer's day collective events like Social Engineers, Technical Skit, Humorous Video on Engineer’s Life, Technical Fault Hunter, Quiz and Project Exhibition.} % Organization/group
	{AbuRoad} % Location
	{Sep. 2017} % Date(s)
	
%---------------------------------------------------------
  \cvhonor
	{Tarunya} % Affiliation/role
	{Winner of the Photography Competition. Participated in various Technical Events.} % Organization/group
	{AbuRoad} % Location
	{Apr 2016,17} % Date(s)

%---------------------------------------------------------
\end{cvhonors}
