%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
   \cventry
	{Intern} % Job title
	{\href{https://www.netcomedu.in/}{CDAC ATC NETCOM}} % Organization
	{Jaipur, India} % Location
	{May - June 2019} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Developed the Intern Management System for the organization.}
		\end{cvitems}
	}
%---------------------------------------------------------
   \cventry
	{\href{https://drive.google.com/drive/folders/1ctuMmFRSP18U_TrqjrOVWXxJXEicQn5n?usp=sharing}{IT Engineer and Core Developer}} % Job title
	{\href{http://citabu.ac.in/}{Chartered Institute of Technology}} % Organization
	{AbuRoad, India} % Location
	{July 2016 - May 2019} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Assisting students in LAB. \href{https://drive.google.com/file/d/18N3tDH6cItm0-5Dkw8gW-p5XGmcwv5ZD/view?usp=sharing}{Designing brochures, pamphlets, souvenirs for an event.}}
			\item {Managing college intranet (pfSense). Developing and Managing - ERP and other softwares for the college digitalization.}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
    {\href{https://drive.google.com/file/d/1X72NUqYnieA3N9TpMftnJDDAonjViYNe/view?usp=sharing}{Campus Ambassador}} % Job title
    {\href{http://hasura.io}{Hasura}} % Organization
    {India} % Location
    {Jan - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing Hasura Developer Groups, Partnership with hackathons.}
        \item {Mentorship at hackathons/other coding events, Engagement with other developer communities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://drive.google.com/drive/folders/1fHcp1yWXWVQ38b3Fh2yb8fttpHtSpiQc?usp=sharing}{Insternshala Student Partner}} % Job title
    {\href{https://internshala.com/}{Internshala}} % Organization
    {India} % Location
    {Aug. 2017 - Mar 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As an ISP I have learnt - Campaigning, Seminar, Social Media Activities, Traffic Generation, Training.}
        \item {Learned to lead from the front and develop essential skills like marketing, communication while representing Internshala in college campus. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Intern} % Job title
    {ThinkTree - Where Ideas Breath} % Organization
    {Indore, India} % Location
    {May - July 2017 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Got to know the different philosophy of art, creativity and software.}
        \item {Worked on different aspects of media like graphics, outdoor advertising, website developing, branding, campaigning, corporate identity etc.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
